\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-12 paper.qmd
Added Figure 12 title

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 10
#| fig-width: 10
#| fig-pos: H
#| fig-cap: "All \\gD{} layouts exhibit high error in the sparse end. The three \\gD{} layouts are: (a) tSNE, (b) UMAP, and (c) PaCMaP, which represent a C-shaped dense cluster colored according to the high-dimensional absolute error. Darker colors indicate high error, while lighter colors indicate low error. Regardless of the NLDR method used, the dense end of the structure shows low error, whereas the sparse end displays high error."

>>>>

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 10
#| fig-width: 10
#| fig-pos: H
#| fig-cap: "The sparse end of the structure exhibits a high model error, while the dense end shows a low model error. The tSNE layouts of the C-shaped cluster, with uniform points (a1) and dense points (b1), along with their selected projections (a2 and b2), are displayed. Darker colors represent a high error, while lighter colors indicate a low error. The uniformly distributed points demonstrate random model errors throughout the structure, whereas the dense structure shows large model error at the sparse end."

### 2025-01-12 paper.tex
Added Figure 12 title

\caption{\label{fig-one-dens_clust-error}All \gD{} layouts exhibit high
error in the sparse end. The three \gD{} layouts are: (a) tSNE, (b)
UMAP, and (c) PaCMaP, which represent a C-shaped dense cluster colored
according to the high-dimensional absolute error. Darker colors indicate
high error, while lighter colors indicate low error. Regardless of the
NLDR method used, the dense end of the structure shows low error,
whereas the sparse end displays high error.}

>>>>

\caption{\label{fig-one-dens_clust-error}The sparse end of the structure
exhibits a high model error, while the dense end shows a low model
error. The tSNE layouts of the C-shaped cluster, with uniform points
(a1) and dense points (b1), along with their selected projections (a2
and b2), are displayed. Darker colors represent a high error, while
lighter colors indicate a low error. The uniformly distributed points
demonstrate random model errors throughout the structure, whereas the
dense structure shows large model error at the sparse end.}
